AA Distributed Software Development Methodology

### 2012-04-18 paper.tex

>>>>

\section{AA Site Report}

\begin{figure}
\begin{center}
   \includegraphics[width=0.8\linewidth,keepaspectratio=true]{figs/aa-0.1.png}
\end{center}
   \caption{
   AA Version 0.1
   }
\label{fig:mm}
\end{figure}

All AA reports made by the developers are sent to a web site and become public,
being possible then for a manager or another developer to follow very closely
the work of a developer, nearly real-time, reading each of his small reports of
what he is doing.

Another possibility is to check older sessions to see when sometimes was done
and the comments of the developer about it, since each AA post happens in a
very small timeframe of work, the information about what was done become very
easy to understand, instead of only of report in the end of a session.

The site is where the developer can add to his session a link for his
screencast about that session, a video summary of what was done to complement
the reports, useful specially on cases where the small reports were done in a
hurry, because the developer didn't want to lose his focus on something
important at that moment.

\secion{Validation}

Each developer AA Session must be validated by another developer, it means that
all reports are read by someone that will consider then valid as reports for
that session of work, so the session doesn't gets lost on the site, the
developer in charge of validating a session is decided randomly.
